---
title: "Presentación Revealjs"
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Diapositiva con un gráfico

```{r, echo=FALSE}
plot(cars)
```

## Gráfico con ggplot2

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
iris %>% ggplot(aes(x = Sepal.Length, y = Petal.Length, shape=Species,col=Species))+geom_point(size=4)

```

## Mapa interactivo con Leaflet (Presenta problemas)

```{r out.width='100%', fig.height=6, eval=require('leaflet'), echo=FALSE}
library(leaflet)
leaflet() %>% addTiles() %>% setView(-74.0841, 4.63858, zoom = 16)
```

## Tabla interactiva con DT

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(DT)
datatable(iris)
```


